### 2011-10-30 doc/theses/vitasek/chapter-4-1-experiments-setup.tex
Thesis: in progress.

% TODO I cannot stress this enough times: make sure there is an explanation of heuristics notation used in pseudocode listing, SOMEWHERE

@@

From 3 different sources we collected 6 different data sets, called \dataset{OVA1} - \dataset{OVA3}, \dataset{XMA-c}, \dataset{XMA-p} and \dataset{XMD}. Their summary is Table \ref{table-experiments-data-realistic}, their graph representations can be seen in Figure \ref{image-experiments-data-realistic}. Because the legal status of disclosing these data sets is unclear, we will refrain from identifying them beyond these artificial identifiers. Neither will they be included on the DVD distributed with this thesis.

@@

We used 2 data sets to convert, \dataset{MSH} and \dataset{NTH}. Unfortunately, the same problem with disclosure as in the previous case applies here. None of these sets had any attributes before the conversion. Their summary is Table \ref{table-experiments-data-converted}, their graphs are in Figure \ref{image-experiments-data-converted}.

@@

We now have to introduce a few notions before moving forward to the description of our experiments.\\

>>>>

@@

From 3 different sources we collected 6 different data sets, called \dataset{OVA1} - \dataset{OVA3}, \dataset{XMA-c}, \dataset{XMA-p} and \dataset{XMD}. Their summary is Table \ref{table-experiments-data-realistic}, their graph representations can be seen in Figure \ref{image-experiments-data-realistic}. Because the legal status of disclosing these data sets is unclear, we will refrain from identifying them beyond these artificial identifiers. The DVD distributed with this thesis will contain their anonymized version.

@@

We used 2 data sets to convert, \dataset{MSH} and \dataset{NTH}. Unfortunately, the same problem with disclosure as in the previous case applies here, the DVD contains the anonymized version again. None of these sets had any attributes before the conversion. Their summary is Table \ref{table-experiments-data-converted}, their graphs are in Figure \ref{image-experiments-data-converted}.

@@

We now have to introduce a few notions before moving forward to the description of our experiments. In the following text, words \textit{experiment} and \textit{experimental} in various phrases (\textit{experiment X}, \textit{experimental Y}) will be used interchangeably.\\
